---
title: "Some Tools for Understanding Drift Diffusion Models"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Some Tools for Understanding Drift Diffusion Models}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  warning = FALSE,
  comment = "#>"
)
```

```{r setup}
library(ggplot2)
library(dplyr)
library(norbertr)
```

## Simulating a drift diffusion model

Here, we draw 10000 samples from a drift diffusion model with relative starting point $b = 0.5$, inter-barrier distance $a = 2$, and drift rate of $v = 0.5$.
In this model, we assume a non-decision time period of 0.
```{r}
ddm_sims <- simulate_ddm(10000, b = 0.5, a = 2, v = 0.5)
```

Here, a histogram of response times for each choice.
In typical style, we plot the times corresponding to choices of 0 using negative times.
```{r, fig.width=6, fig.align='center'}
ddm_sims %>% 
  mutate(time = if_else(choice == 1, time, -time)) %>% 
  ggplot(aes(x = time, fill = factor(choice))) + 
  geom_histogram(bins = 100, position = 'identity') +
  xlim(-5, 5) +
  theme_classic()
```

## Bivariate density of response time and response choice

The bivariate density of any given response time and either one of the two alternative choices, given values for $b$, $a$, and $v$, i.e.
$$
\mathrm{P}(t, x \vert b, a, v)
$$
is calculated with `time_choice_density`.
For example, the probability density of a response time of $2.5$ and choice of $1$ given the above parameter values is
```{r}
time_choice_density(t = 2.5, b = 0.5, a = 2, v = 0.5, choice = 1)
```
On the other hand, the probability density of a response time of $1.5$ and choice of $0$ given the above parameter values is
```{r}
time_choice_density(t = 1.5, b = 0.5, a = 2, v = 0.5, choice = 0)
```



