---
title: "Bayesian inference of a drift diffusion model"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Bayesian inference of a drift diffusion model}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  warning = FALSE
)
```

Here's a Stan model for inferring the relative starting point, drift rate and inter-barrier distance of the drift diffusion model. 
This assumes those three values are fixed, though unknown.
In other words, those values do not vary with predictor variables.
In practice, of course, we want these parameters to vary with predictors as in a typical regression model.
This model is intended as just a simple demo of inference in a non-regression model drift diffusion model.
```{r, results='asis', comment='', echo=FALSE}
cat('```stan\n')
cat(readLines(system.file("stan", "ddm.stan", package = 'norbertr')), sep='\n')
cat('```')
```

This model is called by `norbertr::ddm_stan`.
Here it is in practice.

```{r, results='hide'}
library(norbertr)
library(tidyverse)

set.seed(10101)

sims_df <- simulate_ddm(1000, b = 0.75, a = 2, v = 0.5) %>%
  dplyr::mutate(time = time + 0.1)

M <- ddm_stan(time + choice ~ 1, data = sims_df, cores = 4)
```

And the results:
```{r}
M
```

